Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-05-05 doc/main_jfm.tex
adding some texts

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\hypersetup{
    colorlinks = true,
    urlcolor   = blue,
    citecolor  = black,
}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newcommand{\RomanNumeralCaps}[1]
\linenumbers

@@

The preliminary test of the proposed numerical algorithm is the Jeffery orbits of single ellipsoidal particle under a shear flow. A particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is $\chi = 0^\circ$. Based on the theoretical Jeffery orbits,

\begin{equation}
\chi = \tan^{-1}\left(\frac{a}{b}\left(\tan \frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
\end{equation}
%
where $a$, $b$ are semi-major and semi-minor axes, $\dot\gamma$ is the shear rate, and the test aspect ratio of the particle is $2$. Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from Jeffery orbits.

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{JefferyOrbit.eps}
\end{center}
  \caption{Comparison of the target angle $\chi(t)$ versus time $t$ between the theoretical Jeffery orbit and the result from the integral equation method.
  }
    \label{figure1}
\end{figure}

@@

To study the deformation of the closed bilayer structure under a shear flow using the proposed algorithm, 
we adopt a widely tested numerical simulation in both continuum and molecular dynamics models. The well known results indicate that the vesicle does tank-treading when there is no viscosity contrast in both inside and outside of the structure.
Given a set of various shear rates, with no viscosity difference between internal and external fluids, 
the vesicle-like granular structure is initially placed in a quiescent flow for obtaining an equilibrium shape.

\begin{figure}
\begin{center}
\includegraphics[width=0.3\textwidth]{N58_0.eps}
\includegraphics[width=0.3\textwidth]{N58_20000.eps}
\end{center}
  \caption{Vesicle under a shear flow where the shear rate $\dot\gamma=0.005$: 
  (a) Initial configuration of 58-body vesicle; (b) Deformed vesicle.
  }
    \label{figure2}
\end{figure}

@@

@@

With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations.

\begin{figure}
\begin{center}
\includegraphics[width=0.4\textwidth]{N58_rupt_0.eps}
\includegraphics[width=0.4\textwidth]{N58_rupt_200.eps}\\
\includegraphics[width=0.4\textwidth]{N58_rupt_400.eps}
\includegraphics[width=0.4\textwidth]{N58_rupt_600.eps}
\end{center}
  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold. Here the shear rate is $\dot\gamma = 0.1$.
  }
    \label{figure3}
\end{figure}

@@

Figure~\ref{figure4} shows two sets of simulations. Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow. The flow is stretching along the $y$ direction and squeezing in $x$ direction. Hence two vesicles are first pushed toward each other  then separate. With the same starting state, panels (e)-(h) are the observed phenomena when two vesicles are in a shear flow $x = \dot\gamma y$. An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned.

\begin{figure}
\begin{center}
\includegraphics[width=0.22\textwidth]{N116_ext_0.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_2500.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_5000.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_7500.eps}\\
\includegraphics[width=0.22\textwidth]{N116_shear_3000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_6000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_9000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_12000.eps}
\end{center}
  \caption{Two vesicles under a linear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a) and two sets of simulation results are two vesicles under 
  (b)-(d) extensional flow and (e)-(h) shear flow. 
  }
    \label{figure4}
\end{figure}

>>>>

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{float}

\hypersetup{
    colorlinks = true,
    urlcolor   = blue,
    citecolor  = black,
}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newcommand{\RomanNumeralCaps}[1]
\linenumbers

@@

The preliminary test of the proposed model using integral equation method is the Jeffery orbits of single ellipsoidal particle under a shear flow. A particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\chi = 0^\circ$. Based on the theoretical Jeffery orbits with respect to the target angle,

\begin{equation}
\chi(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
\end{equation}
%
where $a$, $b$ are semi-major and semi-minor axes, $\dot\gamma$ is the shear rate, and the test aspect ratio of the particle is $2$. Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from Jeffery orbits.

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.5\textwidth]{JefferyOrbit.eps}
\end{center}
  \caption{Comparison of the target angle $\chi(t)$ versus time $t$ between the theoretical Jeffery orbit and the result from the integral equation method. The schematic of the simulation setup is shown in the inset of the figure.
  }
    \label{figure1}
\end{figure}

@@

To study the deformation of a closed bilayer structure under a shear flow using the proposed algorithm, 
we adopt a widely tested numerical simulation, single vesicle under a shear flow, in both continuum and molecular dynamics models. The well known results indicate that the vesicle does tank-treading when there is no viscosity contrast in both inside and outside of the structure.
Given a set of various shear rates, with no viscosity difference between internal and external fluids, 
the vesicle-like granular structure is initially placed in a quiescent flow for obtaining an equilibrium shape.

The starting center of mass position of the vesicle is pinned at the origin and Figure~\ref{figure2} shows 
the initial circular shape  and the deformed configuration of the vesicle after a period of time. 
The reduced area is shown in Figure~\ref{figure3} where we compare the change of area over the time with two different shear rates.

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.3\textwidth]{N58_0.eps}
\includegraphics[width=0.3\textwidth]{N58_20000.eps}
\end{center}
  \caption{Vesicle under a shear flow where the shear rate $\dot\gamma=0.005$: 
  (a) Initial configuration of 58-body vesicle; (b) Deformed vesicle.
  }
    \label{figure2}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.4\textwidth]{ReducedArea.eps}
\end{center} 
  \caption{Reduced area transitions over time. The slower shear rate generates a faster convergence in the reduced area. 
  }
    \label{figure3}
\end{figure}

@@

With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations. Figure~\ref{figure4} shows a demonstration of a vesicle under a shear flow with shear rate $\dot\gamma=0.1$.

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.4\textwidth]{N58_rupt_0.eps}
\includegraphics[width=0.4\textwidth]{N58_rupt_200.eps}\\
\includegraphics[width=0.4\textwidth]{N58_rupt_400.eps}
\includegraphics[width=0.4\textwidth]{N58_rupt_600.eps}
\end{center}
  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold. Here the shear rate is $\dot\gamma = 0.1$. Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)). (c)-(d) are the later states during the simulation.
  }
    \label{figure4}
\end{figure}

@@

Figure~\ref{figure5} shows two sets of simulations. Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow. The flow is stretching along the $y$ direction and squeezing in $x$ direction. Hence two vesicles are first pushed toward each other  then separate. With the same starting state, panels (e)-(h) are the observed phenomena when two vesicles are in a shear flow $x = \dot\gamma y$. An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned.

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.22\textwidth]{N116_ext_0.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_2500.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_5000.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_7500.eps}\\
\includegraphics[width=0.22\textwidth]{N116_shear_3000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_6000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_9000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_12000.eps}
\end{center}
  \caption{Two vesicles under a linear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a) and two sets of simulation results are two vesicles under: 
  (b)-(d) extensional flow and (e)-(h) shear flow. 
  }
    \label{figure5}
\end{figure}
